---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nflverse-data

<!-- badges: start -->
<!-- badges: end -->

This repository holds automated data releases for nflverse projects (i.e. all of the data powered/scraped via GitHub Actions). 

## Usage

You can download data hosted here with the `{nflreadr}` package, or manually download and access the [releases](https://github.com/nflverse/nflverse-data/releases) page. Releases are roughly organized along the [main functions](https://nflreadr.nflverse.com/reference/) of nflreadr.

## Automation Status

The following table reports on the status and last update times of nflverse data pipelines.

```{r echo = FALSE, message = FALSE, warning = FALSE}
# piggyback::pb_list() |>
#   dplyr::filter(file_name %in% c("timestamp.json","")) |>
#   dplyr::distinct(tag,file_name) |> 
#   saveRDS("man/data_releases.rds")

update_times <- readRDS("man/data_releases.rds") |> 
  dplyr::mutate(url = glue::glue("https://github.com/nflverse/nflverse-data/releases/download/{tag}/timestamp.json"),
         badge = glue::glue("[![{tag}](https://img.shields.io/badge/dynamic/json?color=blue&label={paste0('load_',tag)}&query=last_updated&style=flat-square&url={URLencode(url)})](https://github.com/nflverse/nflverse-data/releases/tag/{tag})")) |> 
  dplyr::select(
    Data = tag,
    `Last Updated` = badge
  ) |> 
  dplyr::bind_rows(
    list(Data = "pbp_raw", `Last Updated` = "[![raw pbp data](https://img.shields.io/github/last-commit/nflverse/nflfastR-raw?label=Raw%20PBP%20Updated&style=flat-square)]()")
  )

status <- tibble::tribble(
  ~Data, ~ Status,
  "pbp_raw", "",
  "pbp", "![pbp and ps](https://img.shields.io/github/workflow/status/nflverse/nflfastR-data/update_current_season_pbp_and_stats?label=pbp_status&style=flat-square)",
  "player_stats", "![pbp and ps](https://img.shields.io/github/workflow/status/nflverse/nflfastR-data/update_current_season_pbp_and_stats?label=ps_status&style=flat-square)",
  "rosters", "![rosters](https://img.shields.io/github/workflow/status/nflverse/nflfastR-roster/update_rosters?label=rosters_status&style=flat-square)",
  "snap_counts", "![snap_counts](https://img.shields.io/github/workflow/status/nflverse/pfr_scrapR/update_snap_counts?label=snaps_status&style=flat-square)",
  "pfr_advstats", "![adv_stats](https://img.shields.io/github/workflow/status/nflverse/pfr_scrapR/update_adv_stats?label=advstats_status&style=flat-square)",
  "nextgen_stats", "![ngs](https://img.shields.io/github/workflow/status/nflverse/ngs-data/update_ngs?label=ngs_status&style=flat-square)",
  "injuries", "",
  "depth_charts", "",
  "combine", "",
  "nfl4th", "![nfl4th](https://img.shields.io/github/workflow/status/nflverse/nfl4th/update-computed-numbers?label=nfl4th_precompute&style=flat-square)",
  "ffverse player IDs", "![weekly-playerids](https://img.shields.io/github/workflow/status/dynastyprocess/data/weekly-playerids?label=ff_playerids&style=flat-square)",
  "ffverse rankings", "![weekly-fantasypros](https://img.shields.io/github/workflow/status/dynastyprocess/data/weekly-fantasypros?label=rankings&style=flat-square)"
  ) |> 
  dplyr::left_join(update_times, by = "Data") |> 
  dplyr::mutate_all(tidyr::replace_na,"") |> 
  dplyr::mutate(Status = glue::glue("[{Status}]()"))
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
knitr::kable(status)
```

```{asis include = FALSE}

### Play by Play

![raw](https://img.shields.io/github/last-commit/nflverse/nflfastR-raw?label=Raw%20PBP%20Updated&style=flat-square)

Raw JSON should appear 1-2 hours after each game.

![pbp and ps](https://img.shields.io/github/workflow/status/nflverse/nflfastR-data/update_current_season_pbp_and_stats?label=PBP%20%26%20Player%20Stats&style=flat-square)

PBP and PS are updated at 9:00 UTC each day from September to February

### Rosters
![rosters](https://img.shields.io/github/workflow/status/nflverse/nflfastR-roster/update_rosters?label=Rosters&style=flat-square)

Rosters are updated at 7:00 UTC each day.

### Snap Counts
![snap_counts](https://img.shields.io/github/workflow/status/nflverse/pfr_scrapR/update_snap_counts?label=Snap%20Counts&style=flat-square)

Snap counts are polled four times a day for new data.

### Advanced Pass/Rush/Rec/Def Stats

![adv_stats](https://img.shields.io/github/workflow/status/nflverse/pfr_scrapR/update_adv_stats?label=PFR%20Adv%20Stats&style=flat-square)

Advanced Stats are polled four times a day for new data.

### Next Gen Stats

![ngs](https://img.shields.io/github/workflow/status/nflverse/ngs-data/update_ngs?label=NGS%20data&style=flat-square)

NGS is polled every day at 7:00 UTC from September to February.

### nfl4th

![nfl4th](https://img.shields.io/github/workflow/status/nflverse/nfl4th/update-computed-numbers?label=nfl4th_precompute&style=flat-square)

nfl4th's precomputed numbers are rebuilt each day at 7:00 UTC from September to February.

### ffverse player IDs
![weekly-playerids](https://img.shields.io/github/workflow/status/dynastyprocess/data/weekly-playerids?label=ff_playerids&style=flat-square)

This is updated on a weekly basis.

### ffverse rankings
![weekly-fantasypros](https://img.shields.io/github/workflow/status/dynastyprocess/data/weekly-fantasypros?label=rankings&style=flat-square)

This is updated on Thursdays at 7:00 pm ET. 

```

